### 2010-09-13 Thesis/TitlePage.tex
- Update 13 September -
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@174 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\vspace*{2.5cm}
\Huge \textbf{Real-time Soft Tissue Modelling on GPU for Medical Simulation} \\
\vspace*{2.5cm}
\noindent \large Prepared by Olivier \textsc{Comas} at \\ 
INRIA Lille, \textsc{Shaman} Team and CSIRO ICT Brisbane, AEHRC \\
\vspace*{0.5cm}
\noindent \large \color{red}{DRAFT - \today ~at \currenttime} \\
%\noindent \large Defended on the $00^{th}$ of December 2010 \\
\end{center}
\vspace*{1cm}
\noindent \large \textbf{Jury:} \\
\begin{center}
\noindent \large 
\begin{tabular}{llcl}
      \textit{Reviewers:}	& Thomas Sangild \textsc{S\o rensen}          & - & University of Aarhus, Denmark\\
				& Bernard \textsc{}		& - & INRIA (Shaman)\\
      \textit{Advisor:}	& Stéphane \textsc{Cotin}		& - & INRIA (Shaman), France\\
      \textit{President:}	& Bernard \textsc{}		& - & INRIA (Shaman)\\
      \textit{Examinators:}   & Bernard \textsc{}          & - & INRIA (Shaman)\\
      				& Bernard \textsc{}			& - & INRIA (Shaman)\\
\end{tabular}
\end{center}
\end{titlepage}
\sloppy

>>>>

\vspace*{2.5cm}
\Huge \textbf{Real-time Soft Tissue Modelling on GPU for Medical Simulation} \\
\vspace*{2.5cm}
\noindent \large Prepared by Olivier \textsc{Comas} at \\ 
INRIA Lille, \textsc{Shaman} Team and CSIRO ICT Brisbane, AEHRC \\
\vspace*{0.5cm}
\noindent \large \color{red}{DRAFT - \today ~at \currenttime} \\
%\noindent \large Defended on the $00^{th}$ of December 2010 \\
\end{center}
\vspace*{1cm}
\noindent \large \textbf{Jury:} \\
\begin{center}
\noindent \large 
\begin{tabular}{llcl}
      \textit{Reviewers:}	& Thomas Sangild \textsc{S\o rensen}          & - & University of Aarhus, Denmark\\
				& Georges \textsc{Dumont}		& - & INRIA (Bunraku team), Rennes, France\\
      \textit{Advisor:}	& Stéphane \textsc{Cotin}		& - & INRIA (Shaman team), Lille, France\\
      \textit{President:}	& Laurent \textsc{Grisoni}		& - & INRIA (Mint team), Lille, France\\
      \textit{Examinators:}   & Tamy \textsc{Boubekeur}          & - & Telecom ParisTech, Paris, France\\
      				& Bernard \textsc{}			& - & INRIA (Shaman)\\
\end{tabular}
\end{center}
\end{titlepage}
\sloppy
